%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Simple LaTeX CV Template %%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%% Document Setup %%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't like 10pt? Try 11pt or 12pt
\documentclass[10pt]{article}

% This is a helpful package that puts math inside length specifications
\usepackage{calc}
\usepackage{graphicx}

% Simpler bibsection for CV sections
% (thanks to natbib for inspiration)
\makeatletter
\newlength{\bibhang}
\setlength{\bibhang}{1em}
\newlength{\bibsep}
 {\@listi \global\bibsep\itemsep \global\advance\bibsep by\parsep}
\newenvironment{bibsection}%
        {\vspace{-\baselineskip}\begin{list}{}{%
       \setlength{\leftmargin}{\bibhang}%
       \setlength{\itemindent}{-\leftmargin}%
       \setlength{\itemsep}{\bibsep}%
       \setlength{\parsep}{\z@}%
        \setlength{\partopsep}{0pt}%
        \setlength{\topsep}{0pt}}}
        {\end{list}\vspace{-.6\baselineskip}}
\makeatother

% Layout: Puts the section titles on left side of page
\reversemarginpar

%
%         PAPER SIZE, PAGE NUMBER, AND DOCUMENT LAYOUT NOTES: 
%
% The next \usepackage line changes the layout for CV style section
% headings as marginal notes. It also sets up the paper size as either
% letter or A4. By default, letter was used. If A4 paper is desired,
% comment out the letterpaper lines and uncomment the a4paper lines.
%
% As you can see, the margin widths and section title widths can be
% easily adjusted.
%
% ALSO: Notice that the includefoot option can be commented OUT in order
% to put the PAGE NUMBER *IN* the bottom margin. This will make the
% effective text area larger.
%
% IF YOU WISH TO REMOVE THE ``of LASTPAGE'' next to each page number,
% see the note about the +LP and -LP lines below. Comment out the +LP
% and uncomment the -LP.
%
% IF YOU WISH TO REMOVE PAGE NUMBERS, be sure that the includefoot line
% is uncommented and ALSO uncomment the \pagestyle{empty} a few lines
% below.
%

%% Use these lines for letter-sized paper
\usepackage[paper=letterpaper,
            %includefoot, % Uncomment to put page number above margin
            marginparwidth=1.2in,     % Length of section titles
            marginparsep=.05in,       % Space between titles and text
            margin=0.3in,               % 0.3 inch margins
            includemp]{geometry}

%% Use these lines for A4-sized paper
%\usepackage[paper=a4paper,
%            %includefoot, % Uncomment to put page number above margin
%            marginparwidth=30.5mm,    % Length of section titles
%            marginparsep=1.5mm,       % Space between titles and text
%            margin=25mm,              % 25mm margins
%            includemp]{geometry}

%% More layout: Get rid of indenting throughout entire document
\setlength{\parindent}{0in}

%% This gives us fun enumeration environments. compactitem will be nice.
\usepackage{paralist}

%% Reference the last page in the page number
%
% NOTE: comment the +LP line and uncomment the -LP line to have page
%       numbers without the ``of ##'' last page reference)
%
% NOTE: uncomment the \pagestyle{empty} line to get rid of all page
%       numbers (make sure includefoot is commented out above)
%
\usepackage{graphicx}
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
%\pagestyle{empty}      % Uncomment this to get rid of page numbers
\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\fancyfootoffset{\marginparsep+\marginparwidth}
\newlength{\footpageshift}
\setlength{\footpageshift}
          {0.5\textwidth+0.5\marginparsep+0.5\marginparwidth-2in}
\lfoot{\hspace{\footpageshift}%
       \parbox{4in}{\, \hfill %
                   % \arabic{page} of \protect\pageref*{LastPage} % +LP
                   \arabic{page}                               % -LP
                    \hfill \,}}

% Finally, give us PDF bookmarks
%
\usepackage{color,hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}

%%%%%%%%%%%%%%%%%%%%%%%% End Document Setup %%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%% Helper Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%%

% The title (name) with a horizontal rule under it
%
% Usage: \makeheading{name}
%
% Place at top of document. It should be the first thing.
\newcommand{\makeheading}[1]%
        {\hspace*{-\marginparsep minus \marginparwidth}%
         \begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
                {\large \bfseries #1}\\[-0.15\baselineskip]%
                 \rule{\columnwidth}{1pt}%
         \end{minipage}}

% The section headings
%
% Usage: \section{section name}
%
% Follow this section IMMEDIATELY with the first line of the section
% text. Do not put whitespace in between. That is, do this: 
%
%       \section{My Information}
%       Here is my information.
%
% and NOT this: 
%
%       \section{My Information}
%
%       Here is my information.
%
% Otherwise the top of the section header will not line up with the top
% of the section. Of course, using a single comment character (%) on
% empty lines allows for the function of the first example with the
% readability of the second example.
\renewcommand{\section}[2]%
        {\pagebreak[2]\vspace{1.3\baselineskip}%
         \phantomsection\addcontentsline{toc}{section}{#1}%
         \hspace{0in}%
         \marginpar{
         \raggedright \scshape #1}#2}

% An itemize-style list with lots of space between items
\newenvironment{outerlist}[1][\enskip\textbullet]%
        {\begin{itemize}[#1]}{\end{itemize}%
         \vspace{-.6\baselineskip}}

% An environment IDENTICAL to outerlist that has better pre-list spacing
% when used as the first thing in a \section
\newenvironment{lonelist}[1][\enskip\textbullet]%
        {\vspace{-\baselineskip}\begin{list}{#1}{%
        \setlength{\partopsep}{0pt}%
        \setlength{\topsep}{0pt}}}
        {\end{list}\vspace{-.6\baselineskip}}

% An itemize-style list with little space between items
\newenvironment{innerlist}[1][\enskip\textbullet]%
        {\begin{compactitem}[#1]}{\end{compactitem}}

% An environment IDENTICAL to innerlist that has better pre-list spacing
% when used as the first thing in a \section
\newenvironment{loneinnerlist}[1][\enskip\textbullet]%
        {\vspace{-\baselineskip}\begin{compactitem}[#1]}
        {\end{compactitem}\vspace{-.6\baselineskip}}

% To add some paragraph space between lines.
% This also tells LaTeX to preferably break a page on one of these gaps
% if there is a needed pagebreak nearby.
\newcommand{\blankline}{\quad\pagebreak[2]}

% Uses hyperref to link DOI
\newcommand\doilink[1]{\href{http: //dx.doi.org/#1}{#1}}
\newcommand\doi[1]{doi: \doilink{#1}}

% For \url{SOME_URL}, links SOME_URL to the url SOME_URL
\providecommand*\url[1]{\href{#1}{#1}}
% Same as above, but pretty-prints SOME_URL in teletype fixed-width font
\renewcommand*\url[1]{\href{#1}{\texttt{#1}}}

% For \email{ADDRESS}, links ADDRESS to the url mailto: ADDRESS
\providecommand*\email[1]{\href{mailto: #1}{#1}}
% Same as above, but pretty-prints ADDRESS in teletype fixed-width font
%\renewcommand*\email[1]{\href{mailto: #1}{\texttt{#1}}}

%%%%%%%%%%%%%%%%%%%%%%%% End Helper Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%% Begin CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}


\begin{document}
\vspace*{0.1in}

\makeheading{
\flushright{{\huge
Rudradev Sengupta}
\vspace{0.01in}
\\{\Large Curriculum Vitae}
}
}

\section{Contact Information}

\begin{tabular}{@{}p{0.5in}p{3in}p{0.18in}p{0.35in}p{2in}}
Address: & E101, Interuniversity Institute for Biostatistics and Statistical Bioinformatics (I-BioStat), & & Email: & \href{mailto: rudradev.sengupta@uhasselt.be}{rudradev.sengupta@uhasselt.be} \newline \href{mailto: rudradevsengupta@gmail.com}{rudradevsengupta@gmail.com}\\
               & Center for Statistics, Hasselt University, & & Tel: & +32-478013794\\
               & 3590 Diepenbeek, Belgium. & & DOB: & 06.06.1990\\ 
\end{tabular}

\section{Research Interests}

\begin{innerlist}
\item {\textbf{Statistical Bioinformatics}}: Microbiome data analysis, Data mining and machine learning techniques, Multi-source data integration, Exploration and analysis of high-dimensional datasets, Identification of molecular biomarkers, Clustering and biclustering analysis, Time-series analysis.
\vspace{0.1cm}
\item {\textbf{Biostatistics}}: Multivariate data analysis, Longitudinal and clustered data analysis, Bayesian data analysis, Nonlinear modeling, Predictive modeling, Survival data analysis.
\vspace{0.1cm}
\item {\textbf{High Performance Computing}}: Parallel computing, Distributed computing, Cloud computing.
\end{innerlist}

\section{Education}
\href{http: //www.uhasselt.be/en}{\bf Hasselt University (UHasselt)}, Martelarenlaan 42, 3500 Hasselt, Belgium
\begin{innerlist}
\item \emph{Ph.D. in Statistics} (to be graduated: June 2018)\\
\end{innerlist}
\href{http: //www.isical.ac.in/}{\bf Indian Statistical Institute (ISI)}, Kolkata, West Bengal, India
\begin{innerlist}
\item \emph{M.Stat} (graduated with Distinction: June 2013)
\item \emph{B.Stat (Hons.)} (graduated: June 2011)
\end{innerlist}

\blankline

\section{Current Position}
\textbf{Ph.D. Student in \href{https://ibiostat.be/}{I-BioStat}}
\hfill \textbf{June, 2014 to Present}
%
\begin{outerlist}
\item {\textbf{Research Lines}}: 
\begin{innerlist}
\item {\textbf{Integrated Data Analysis in Drug Discovery:}}
\begin{itemize}
\item Model the association between genes and bioactivity data, taking into account the effect of different chemical structures.
\item Using Bayesian Variable Selection to model the monotone relationship between dose and response.
\item High dimensional surrogacy in drug development: single, multiple and partial surrogacy.
\item Different approaches to model dose-response data.
\end{itemize}
\item {\textbf{Microbiome Research:}} 
\begin{itemize}
\item Parametric joint model for microbiome and immunological data, taking care of the treatment effect.
\item Using non-parametric models to take care of zero-inflation in microbiome data.
\item Development of high dimensional microbiome biomarkers for an immune response: hierarchical bayesian approach.
\item Non-linear models and longitudinal analysis of microbiome data.
\item Modeling interaction between OTUs / Families.
\end{itemize}
\item {\textbf{High Performance Computing}}
\begin{itemize}
\item Using VSC cluster in Leuven (Belgium) for faster implementation of different statistical models which helped to do further analysis by reducing the total computational time significantly.
\item Use publicly available resources (e.g. Amazon cloud, Azure etc.) for statistical analysis.
\end{itemize}
\end{innerlist}
\end{outerlist}

\section{Previous Position}
\textbf{Software Engineer/Analyst in \href{http://www.polycom.co.in/}{Polycom}}
\hfill \textbf{August, 2013 to May, 2014}
\newline
\textit{\textbf{Role}}: Software development (using Java) and data analysis (demand forecasting, using R and SQL).

\section{Awards}
\textbf{By Govt. of India}
\begin{innerlist}
\item INSPIRE Scholar, 2008-2011.
\item INSPIRE Scholar, 2011-2013.
\end{innerlist}
\vspace{0.2cm}
\textbf{By Hasselt University Doctoral School}
\begin{innerlist}
\item International and intersectoral mobility grant award, 2016.
\end{innerlist}

\newpage

\section{Publications and Ongoing Research}
\textbf{Journal Articles:}
\begin{innerlist}
\vspace{0.05cm}
\item \href{https://journal.r-project.org/archive/2017/RJ-2017-002/RJ-2017-002.pdf}{IsoGeneGUI: Multiple Approaches for Dose-Response Analysis of Microarray Data Using R (2017)} \newline
\emph{Otava, M., \underline{Sengupta, R.}\footnote{Joint First Author}, Shkedy, Z., Lin, D., Pramana, S., Verbeke, T., Haldermans, P., Hothorn, L.A., Gerhard, D., Kuiper, R.M., Klinglmueller, F. and Kasim, A.}
\vspace{0.05cm}
\item Surrogacy and Biomarker detection in Big Data Environment: An Integrated Analysis of Chemical Structure, Bioactivity and Genetic Information in Drug Discovery (\emph{To be submitted}) \newline
\emph {\underline{Sengupta, R.}}, Shkedy, Z. and Biecek, P.
\vspace{0.05cm}
\item High Dimensional Surrogacy in Drug Development: single, multiple and partial surrogacy - a joint modeling approach (\emph{To be submitted}) \newline
\emph {\underline{Sengupta, R.}} and Shkedy, Z.
\vspace{0.05cm}
\item Development of High Dimensional Microbiome Biomarkers for an Immune Response: Hierarchical Bayesian Approach (\emph{To be submitted}) \newline
\emph {\underline{Sengupta, R.}}, Shkedy, Z., Bijnens, L., Ruiz, V.E., Battaglia, T. and Blaser, M.
\vspace{0.05cm}
\item Development of High-dimensional Microbiome Biomarkers in Small-sample Studies (\emph{To be submitted}) \newline
\emph Perualila-Tan, N.J., \underline{Sengupta, R.}, Shkedy, Z., Bijnens, L., Ruiz, V.E., Battaglia, T. and Blaser, M.
\vspace{0.05cm}
\item \href{https://link.springer.com/article/10.1007/s10623-010-9459-8}{Some observations on HC-128 (2011)} \newline
\emph{Maitra, S., Paul, G., Raizada, S., Sen, S. and \underline{Sengupta, R.}}
\end{innerlist}

\blankline

\textbf{Book Chapters:}
\newline
\href{https://www.crcpress.com/Applied-Biclustering-Methods-for-Big-and-High-Dimensional-Data-Using-R/Kasim-Shkedy-Kaiser-Hochreiter-Talloen/p/book/9781482208238}{{\bf Applied Biclustering Methods for Big and High Dimensional Data Using R (2016)}}
\begin{innerlist}
\item Identification of Local Patterns in the NBA Performance Indicators \newline
\emph{Shkedy, Z., \underline{Sengupta, R.} and Perualila, N.J.}
\vspace{0.05cm}
\item Biclustering for Cloud Computing \newline
\emph{\underline{Sengupta, R.}, Trelles, O., Tirado, O.T. and Shkedy, Z.}
\vspace{0.05cm}
\item The biclustGUI Shiny App \newline
\emph{De Troyer, E., \underline{Sengupta, R.}, Otava, M., Zhang, J.D., Kaiser, S., Culhane, A., Gusenleitner, D., Gestraud, P., Csardi, G., Hochreiter, S., Klambauer, G., Clevert, D.A., Perualila, N.J., Kasim, A. and Shkedy, Z.}
\end{innerlist}

\blankline

\noindent
\href{https://www.crcpress.com/Applied-Surrogate-Endpoint-Evaluation-Methods-with-SAS-and-R/Alonso-Bigirumurame-Burzykowski-Buyse-Molenberghs-Muchene-Perualila-Shkedy-Elst/p/book/9781482249361}{{\bf Applied Surrogate Endpoint Evaluation Methods with SAS and R (2016)}}
\begin{innerlist}
\item High Dimensional Biomarkers in Drug Discovery: The QSTAR Framework \newline
\emph{Perualila, N.J., Shkedy, Z., \underline{Sengupta, R.}, Bigirumurame, T., Bijnens, L., Talloen, W., Verbist, B., G\"{o}hlmann, H.W.H., QSTAR Consortium and Kasim, A.}
\end{innerlist}

\section{Other Research and Professional Internships}
\textbf{Research Visit - \href{http://www.bioinf.jku.at/}{Institute of Bioinformatics, Johannes Kepler University}} \\
Linz, Austria.
\hfill \textbf{14 - 27 June, 2015}
\begin{innerlist}
\item Working with Prof. Oswaldo Trelles' group about using R in Amazon EC2 instance as well as in EMR cluster with EC2 instances as nodes.
\item Automated the cluster creation in Amazon cloud to run R from the browser - no need to have R installed in the laptop.
\item Parallel programing using the computer cluster: faster implementation using the Amazon EMR cluster as compared to the implementation in Laptop and later more things were investigated.
\end{innerlist}

\blankline

\textbf{Research Visit - \href{https://med.nyu.edu/medicine/labs/blaserlab/}{Blaser Lab Group, Langone Medical Center, New York School of Medicine}} \\
New York, USA.
\hfill \textbf{22 - 24 February, 2016}
\begin{innerlist}
\item Working with Prof. Martin Blaser's group on microbiome data analysis. 
\item Ongoing collaboration for future publications.
\end{innerlist}

\blankline

\textbf{Research Visit - \href{https://www.ch.cam.ac.uk/person/ab454}{Unilever Center for Molecular Informatics, Department of Chemistry, University of Cambridge}} \\
Cambridge, UK.
\hfill \textbf{3 - 7 October, 2016}
\begin{innerlist}
\item Working with Prof. Andreas Bender's group about analysing gene-expression data and dose-response analysis of L1000 data. 
\item Ongoing collaboration for future publications.
\end{innerlist}

\blankline

\textbf{Master's Thesis - \href{http://www.isical.ac.in/}{Indian Statistical Institute}} \\
Kolkata, India.
\hfill \textbf{April, 2013 - June, 2013}
\begin{innerlist}
\item Working with Prof. Mandar Mitra's group on evaluation methods for information retrieval systems. 
\item Suggested new statistical approaches to estimate the number of relevant documents corresponding to a particular query.
\end{innerlist}
\newpage

\blankline 

\textbf{Internship - \href{http://www.mzaya.in/}{Mzaya Pvt. Ltd.}} \\
Bangalore, India.
\hfill \textbf{May, 2012 - July, 2012}
\begin{innerlist}
\item Day-ahead exchange price forecasting and solving the Unit Commitment problem.
\item Both \emph{Time Series models} and \emph{Neural Network approach} were adopted to perform day-ahead exchange-price forecasting of power and specifically, the Neural Network based model, produced much better results than general regression models.
\item The electrical unit commitment problem is the problem of optimally deciding which electricity generation units should be running in each period to satisfy a predictably varying demand for electricity. \emph{Genetic Algorithm} was used to deal with this optimization problem.
\end{innerlist}

\blankline

\textbf{Internship - \href{http://ge.geglobalresearch.com/locations/bangalore-india/}{ GE Global Research}} \\
Bangalore, India.
\hfill \textbf{May, 2011 - July, 2011}
\begin{innerlist}
\item Classification of data on change of impedance collected via RFID sensors, using Functional Data Analysis.
\item We managed to find a concrete mathematical function so that better classification, as compared to Principal Component Analysis, can be done, solely based on its parameters.
\end{innerlist}

\section{Software Development}
\textbf{Software Development with \texttt{R}:}
\begin{innerlist}
\item R Packages: \emph{IntegratedJM}, \emph{ORCME}, \emph{IsoGene}, \emph{IsoGeneGUI}.
\item \emph{Biclustering AMI} in Amazon Cloud.
\item Several \emph{ShinyR web applications} in Amazon Cloud.
\end{innerlist}

\section{Teaching Experience}
\textbf{Hasselt University:}
\begin{innerlist}
\item \textbf{Full Course:} Business Statistics for Master of Management; 2016-2017 and 2017-2018.
\item \textbf{Lessons:} Computer Intensive Methods, Master of Biostatistics/ Master of Bioinformatics/ Master of Statistics: Epidemiology \& Public Health Methodology; 2015-2016 and 2016-2017.
\item \textbf{Co-promoter:} Aim\'e Lambert Uwimana, Masters thesis, Master of Statistics, 2016-2017 - \textit{Microbiome Data Analysis: Development of high-dimensional microbiome biomarkers}.
\item \textbf{Supervision:} Pieter Giesen, Project for Analysis of Gene Expression course, Master of Statistics, 2015-2016 - \textit{Analysis of microbiomics data}.
\end{innerlist}

\section{Presentations and Conferences}
\textbf{Conferences:}
\begin{innerlist}
\item Model Based Clustering using Bayesian Variable Selection: Modeling and Computational Issues \newline
\emph{\href{https://events.prace-ri.eu/event/330/}{PRACE Winter School}, Ostrava, Czech Republic; January 12-15, 2015}
\item Development of Microbiome Biomarkers for IgA: a dynamic joint modeling approach\newline
\emph{\href{https://simonsfoundation.emeetingsonline.com/emeetings/websitev2.asp?mmnno=158&pagename=ATTENDEE}{The First Workshop on Challenges in Microbiome Data Analysis - Simons Foundation}, New York, USA; February 24-25, 2016}
\item Model Based Classification of Monotone Gene Profiles using Bayesian Variable Selection \newline
\emph{\href{https://www.bayes-pharma.org/?page_id=1117}{Bayes}, Leuven, Belgium; May 17-20, 2016}
\item Evaluation of Surrogate Endpoint in High Dimensional Data: A Longitudinal Analysis of Family-level Microbial Diversity and Immunoglobulin A \newline
\emph{\href{http://www.ncs-conference.org/?page_id=489}{Non-Clinical Statistics Conference}, Cambridge, UK; October 4-6, 2016}
\item Development of High Dimensional Biomarkers \newline
\emph{\href{https://www.uhasselt.be/channel-network-conference-2017}{IBS Channel Network Conference}, Hasselt, Belgium; April 24-26, 2017}
\item IntegratedJM - an R package to Jointly Model the Gene-Expression and Bioassay Data, Taking Care of the Fingerprint Feature effect \newline
\emph{\href{https://user2017.brussels/}{useR Conference}, Brussels, Belgium; July 4-7, 2017}
\item Development of Microbiome Biomarkers for Immunoglobulin A (IgA): A Joint Modeling Approach \newline
\emph{\href{https://coursesandconferences.wellcomegenomecampus.org/events/item.aspx?e=637}{6th Exploring Human Host-Microbiome Interactions in Health and Disease Meeting}, Hinxton, Cambridge, UK; September 13-15, 2017}
\end{innerlist}

\blankline

\textbf{Other Presentations:}
\begin{innerlist}
\item Cloud Computing and Parallel Programming in Statistical Bioinformatics, using R: Different Case Studies \newline
\emph{ExaScience Project Meeting - IMEC, Belgium; 16.09.2015}
\end{innerlist}

\section{Key Skills}
\textbf{Statistical Modeling and Implementation:}
\begin{innerlist}
\item\textit{\textbf{}}Proficient with mathematical and statistical models as well as computational aspects of modeling.
\item\textit{\textbf{}}Programming languages: Matlab, R, Python, C, C++, Java, SPSS and SAS.
\item\textit{\textbf{}}Prompt in picking up a new computer language or software.
\item\textit{\textbf{}}Good logical reasoning skills.
\item\textit{\textbf{}}Good team player.
\end{innerlist}

\newpage

\blankline 

\blankline

\section{Collaborations}
\begin{tabular}{@{}p{3.5in}p{4in}}
\textbf{Affiliation} & \textbf{Collaborators} \\
& \\
Interuniversity Institute for Biostatistics and Statistical Bioinformatics (I-BioStat), Belgium & Ziv Shkedy, Ewoud de Troyer. \\
Centre for Molecular Science Informatics, Department of Chemistry, University of Cambridge, United Kingdom & Andreas Bender, Avid Afzal. \\
Institute of Bioinformatics, Johannes Kepler University, Linz, Austria & Sepp Hochreiter, G\"unter Klambauer, Djork-Arn{\'e}\newline Clevert. \\
Department of Mathematical Modeling, Statistics and Bioinformatics, Ghent University,Belgium & Olivier Thas, Stijn Hawinkel. \\
Wolfson Research Institute, Durham University, United Kingdom & Adetayo Kasim. \\
Janssen Pharmaceutical Companies of Johnson \& Johnson, Beerse, Belgium & Luc Bijnens, Martin Otava, Nolen Joy Perualila-\newline Tan, Bie Verbist, Willem Talloen, Hinrich W.H.\newline G\"ohlmann, \\
Computer Architecture Department, University of Malaga, Spain & Oswaldo Trelles. \\
Advanced Computing Technologies Unit, RISC Software GmBH, Hagenberg, Austria & Oscar Torreno Tirado. \\
School of Medicine, Pharmacy and Health and Research Design Service (RDS), Durham University, United Kingdom & Theophile Bigirumurame. \\
Department of Statistics - Faculty of Mathematics, Informatics and Statistics, Ludwig-Maximilians, Munich University, Germany & Sebastian Kaiser. \\
Institute of Biostatistics, Leibniz University Hannover, Germany & Ludwig A. Hothorn. \\
GlaxoSmithKline, Belgium & Dan Lin. \\
Sekolah Tinggi Ilmu Statistik/Institute of Statistics, Indonesia and Department of Medical Epidemiology and Biostatistics, Karolinska Institutet, Sweden & Setia Pramana. \\
Open Analytics NV, Belgium & Tobias Verbeke. \\
PXL-IT, PXL University College, Hasselt, Belgium & Philippe Haldermans. \\
School of Mathematics and Statistics, University of Canterbury, New Zealand & Daniel Gerhard. \\
Department of Methodology \& Statistics, Utrecht University, The Netherlands & Rebecca M. Kuiper. \\
Section for Medical Statistics, Center for Medical Statistics and Informatics, Medical University of Vienna, Austria & Florian Klinglmueller. \\
Pharmaceutical Sciences, Translational Technologies and Bioinformatics (PS-TTB), Roche Pharmaceutical Research and Early Development (pRED), Roche Innovation Center, Basel, Switzerland & Jitao David Zhang. \\
Computational Biology and Functional Genomics Laboratory, Harvard School of Public Health, Dana-Farber Cancer Institute, USA & Aedin Culhane. \\
Bioinformatics Program, Boston University, USA & Daniel Gusenleitner. \\
Institut Curie, INSERM U900 and Mines ParisTech, Fontainebleau and Paris, France & Pierre Gestraud. \\
Department of Statistics, Harvard University, USA & Gabor Csardi. \\
Applied Statistics Unit, Indian Statistical Institute, India & Subhamoy Maitra, Goutam Paul. \\
Microsoft Research and The Department of Mathematics, Massachusetts Institute of Technology, USA & Subhabrata Sen. \\
\end{tabular}





\end{document}